---
title: "Draft Figures and Analyses"
author: "Juliette Verstaen"
date: "12/9/2018"
output: pdf_document
toc: true
toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE }

suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
  library(plyr)
})
```

## 1. Plot each fishery B/Bmsy versus F/Fsmy
**Data used**:   updated upside data with Corbett's ITQ/no ITQ data

**Note:** 

- Corbett's ITQ data is only until 2012

- Chris's upside data is now updated until 2016 with the more recent RAM data that Dan had.

**Issues:**

1. Since Corbett's ITQ data is only until 2012, all the fisheries specific data we have past that does not have ITQ data assocaited with them. I made "KOBE" plots with the following data:

    a.  fisheries 1950 - 2012

    b.  fisheries 1950 - 2016

2. Dealing with fisheries with no data on ITQs:
ITQ related analyzes are limited to fisheries that Corbette had data on. I removed the fisheries that have no information on presence or absence of ITQs. I am unsure if this is biasing the data; should we assume that the fisheries with no definate information on ITQs have no ITQs? This seems like it woud be biased as well. 
    - Corbette's ITQ data includes 375 different fisheries years 1950-2012 for a total of ~15,000 lines of data 
    
###a. "KOBE" plots with ITQs not updated past 2012
*All fisheries 1950-2012 *
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  filter(Year >= "1950") %>%
  filter(Year <= "2012")

f_b_itq$rightsbased[f_b_itq$rightsbased == "0"]<- "No ITQ"
f_b_itq$rightsbased[f_b_itq$rightsbased == "1"]<- "ITQ"


ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2012")



```


###b. "KOBE" plots with ITQs updated through 2016
*All fisheries 1950-2016 *
```{r}

ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")

f_b_itq_updated <- ITQ_projection_updated %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  filter(Year >= "1950") %>%
  filter(Year <= "2016")

f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "0"]<- "No ITQ"
f_b_itq_updated$rightsbased[f_b_itq_updated$rightsbased == "1"]<- "ITQ"

ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("Fisheries 1950-2016")


```

##2. Total Global Catch from ITQ, TURF, or No ITQ fisheries

**Data used**:   updated upside data with Corbett's ITQ/no ITQ data

**Notes:** 

- Same issues as before with Corbett data only until 2012
- For analysis through 2016: extracted information about which fisheries had ITQs in 2012 and applied it to the same fisheries into the future. This doesn't take into account other fisheries implement ITQs past 2012, or if fisheries stop ITQs. Only countries with ITQs in 2012 are : Australia, USA, Canda, Japan, Peru, Argentina, South Africa, New Zealand

*The analysis below does not include TURF information from DiscoverTurf GP because that data is not fishery specific enough to merge with the upside/Corbette data*

**technical note for JV: what units is the catch in the upside/rams data?**

###a. Total Catch ITQ, No ITQ, TURF in 2012
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) 

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012") 

itq_2012_rightsbasedTRUE <- filter(countries_itq_2012, rightsbased == "1")

itq_2012_rightsbasedFALSE <- filter(countries_itq_2012, rightsbased == "0")

itq_2012_rightsbasedTURF <- filter(countries_itq_2012, rightsbased == "2")


sum(itq_2012_rightsbasedTRUE$Catch, na.rm = TRUE)
#4,350,545

sum(itq_2012_rightsbasedFALSE$Catch, na.rm = TRUE)
#149,554

sum(itq_2012_rightsbasedTURF$Catch, na.rm = TRUE)
#260,000
```
####**2012 total catch:**

ITQs: 4,350,545

No ITQ: 149,554 (all USA)

TURF: 260,000(all Japan)


###b. Total Catch ITQ, No ITQ, TURF in 2016
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA" & iq != "NA" & ivq != "NA" & turf != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) 

countries_itq_2012_2 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig) %>%
  filter(Year == "2012")  %>%
  select(Country, rightsbased, IdOrig)

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country, Year, Catch)

itq_2016_updated <- join(ITQ_projection_2016, countries_itq_2012_2, by= c("IdOrig", "Country"), type= "full")

itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")

itq_2016_rightsbasedFALSE <- filter(itq_2016_updated, rightsbased == "0")

itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")


sum(itq_2016_rightsbasedTRUE$Catch, na.rm = TRUE)
#20,217,168

sum(itq_2016_rightsbasedFALSE$Catch, na.rm = TRUE)
#1,154,957

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#382,370.4
```

####**2016 total catch:**

ITQs: 20,217,168

No ITQ: 1,154,957 (all in the USA)

TURF: 382,370.4 (all in Japan)



##3. Probability of ITQ 

###itq or turf: probablity of itq = f(ISSCAPP and GDP)
*regression converges*
```{r}

turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

turf_itq_isscaap_mutate <- turf_itq_isscaap %>%
  mutate(i_right = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0")) %>%
  mutate(TURF = case_when(
    turf == TRUE ~ "1", 
    turf = FALSE ~"0"
  )) %>%
  select(SciName, Country, SpeciesCat, i_right, TURF) 


turf_itq_isscaap_mutate$TURF[is.na(turf_itq_isscaap_mutate$TURF)] <- "0"


join_gdp_rightsbased <- merge(gdp, turf_itq_isscaap_mutate, by = c("Country"))

gdp_rightsbased <- filter(join_gdp_rightsbased, SpeciesCat != "NA" )

gdp_rightsbased$SpeciesCat <- factor(gdp_rightsbased$SpeciesCat)
gdp_rightsbased$i_right <- as.numeric(gdp_rightsbased$i_right)

itq_glm <- glm(formula = i_right ~ current_gdp + SpeciesCat, family = "binomial", data = gdp_rightsbased)
itq_glm

summary(itq_glm)

```


##4. Run Turf versus ITQ probably: prob(ITQ). Turf = 1 and ITQ = 0 with the data set that was the turf/itq only one
*regression does not converge*
```{r}
turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

gdp_all <- read_csv("/GitHub/global_fisheries_managment/data/gpd.csv")

gdp <- filter(gdp_all, current_gdp != "NA")

species_rightsbased_mutate_2 <- turf_itq_isscaap %>%
  mutate(rightbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "0",
    turf == TRUE ~ "1"))

gdp <- filter(gdp_all, current_gdp != "NA")

join_gdp_rightsbased_2 <- join(gdp, species_rightsbased_mutate_2, by = c("Country"), type = "full")

gdp_rightsbased_2 <- filter(join_gdp_rightsbased_2, SpeciesCat != "NA" )

gdp_rightsbased_2$SpeciesCat <- factor(gdp_rightsbased_2$SpeciesCat)
gdp_rightsbased_2$rightbased <- as.numeric(gdp_rightsbased_2$rightbased)

rightbased_glm <- glm(formula = rightbased ~ current_gdp + SpeciesCat + programstart, family = "binomial", data = gdp_rightsbased_2)
rightbased_glm

summary(rightbased_glm)

```

##5. MPA Area by Country

*Note: did not filter out MPAs that did no meet IUCN and/or CBD PA definition*

MPA data: from protectedplanet.net
```{r}
mpa_updated <- read_csv("data/mpa_updated.csv") 
```


###MPAs that are completly No Take
The top 10 countries with the largest MPA area (km$$^2$$). These MPAs are 100% no take.
```{r}

##Completly no Take
mpa <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All") %>%
  group_by(Country)

mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
mpa_area

names(mpa_area) <-c("Country", "Area")

mpa_area_10 <- top_n(mpa_area, 10, Area)
mpa_area_10

##all countries
mpa_area_10$Country <- factor(mpa_area_10$Country, levels = mpa_area_10$Country[order(mpa_area_10$Area)])

ggplot(mpa_area_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No Take MPAs")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

###MPAs that are completly No Take
The top 10 countries (minus areas beyond national jurisdiction) with the largest MPA area (km$$^2$$). These MPAs are 100% no take.
```{r}

##Completly no Take
mpa <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All") %>%
  group_by(Country)

mpa_area <- aggregate(mpa$REP_M_AREA, by=list(Country=mpa$Country), FUN=sum)
mpa_area

names(mpa_area) <-c("Country", "Area")

mpa_area_10 <- top_n(mpa_area, 10, Area)
mpa_area_10

#all countries minus areas beyond national jurisdiction
mpa_area_nojurisdiction <-filter(mpa_area, Country != "Areas Beyond National Jurisdiction")
mpa_area_nojurisdiction_10 <- top_n(mpa_area_nojurisdiction, 10, Area)
mpa_area_nojurisdiction_10

mpa_area_nojurisdiction_10$Country <- factor(mpa_area_nojurisdiction_10$Country, levels = mpa_area_nojurisdiction_10$Country[order(mpa_area_nojurisdiction_10$Area)])

ggplot(mpa_area_nojurisdiction_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No Take MPAs (-ABNJ)")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

###MPAs that are completly No Take or Partial No Take
```{r}
##No Take and Partial Take

mpa_parttake <- mpa_updated %>%
  select(Country, REP_M_AREA, MARINE, NO_TAKE) %>%
  filter(MARINE == "2" | MARINE == "1") %>%
  filter(NO_TAKE == "All" | NO_TAKE == "Part") %>%
  group_by(Country)


mpa_area_part <- aggregate(mpa_parttake$REP_M_AREA, by=list(Country=mpa_parttake$Country), FUN=sum)
mpa_area_part

names(mpa_area_part) <-c("Country", "Area")

mpa_area_part_10 <- top_n(mpa_area_part, 10, Area)
mpa_area_part_10

##all countries
mpa_area_part_10$Country <- factor(mpa_area_part_10$Country, levels = mpa_area_part_10$Country[order(mpa_area_part_10$Area)])

ggplot(mpa_area_part_10, aes(x = Country, y = Area)) +
  geom_bar(stat = "identity")+
  ggtitle("Top 10 Countries with No or Partial Take MPAs")+
  coord_flip()+
  theme_bw()+
  ylab("Area km2")

```

